Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-29 exec-model.tex
small edit

Loops and iterations are crucial for several applications. Support for iterations in data-intensive computing systems typically relies on submitting a new job for each iteration or by adding additional nodes to a running DAG \cite{DBLP:journals/pvldb/BuHBE10, DBLP:conf/hotcloud/ZahariaCFSS10}. As depicted in \autoref{fig:iterations}, Flink maintains the DAG-based runtime and scheduler, and allows for special iteration ``head'' and ``tail'' tasks that are implicitly connected with feedback edges. The role of these tasks is to establish an active feedback channel to the DAG and provide coordination for processing data records in transit within this feedback channel. Coordination is needed for implementing any type of structured parallel iteration model such as the Bulk Synchronous Parallel (BSP) model as we explain in section \ref{sec:batch-iterations}.

>>>>

Loops and iterations are crucial for several applications. Support for iterations in data-intensive computing systems typically relies on submitting a new job for each iteration or by adding additional nodes to a running DAG \cite{DBLP:journals/pvldb/BuHBE10, DBLP:conf/hotcloud/ZahariaCFSS10}. Iterations in Flink are implemented as specialized operators that can contain other operators (iteration step) and can be part of the dag. As depicted in \autoref{fig:iterations}, Flink maintains the DAG-based runtime and scheduler, and allows for special iteration ``head'' and ``tail'' tasks that are implicitly connected with feedback edges. The role of these tasks is to establish an active feedback channel to the iteration step and provide coordination for processing data records in transit within this feedback channel. Coordination is needed for implementing any type of structured parallel iteration model such as the Bulk Synchronous Parallel (BSP) model as we explain in section \ref{sec:batch-iterations}.
